\ttitle

### 2013-02-05 Chapters/Chapter2.tex
More on HMM

@@

@@

In \cite{oliver2002layered} it is stated that HMMs are robust mechanisms with 
respect to changes in temporal segmentation of observations, although they 
suffer from a few problems when applied to reason about longer and complexer 
sequences over time. They state that, especially with limited training data, 
the HMM tend to be overfitted and tend to lack structure and have an excess of 
parameters. The overcome this limitation, they introduce a Layered Hidden 
Markov Model (LHHM) which they show is more robust to temporal changes in 
observations. They make use of the hypothesis from the field of psychology, 
that human behavior is hierarchically structured \cite{zacks2001event}.

Viterbi algorithm / path; find the most likely sequence of cause-states for 
the observed measures.

>>>>

*** [fusion of accelerometer data, gyroscopes, magnetic field sensors, 
pressure, microphones, etc]

@@

In \cite{guenterberg2009automatic} a automatic system is used to segment a 
continuous stream of data. By calculating features as activity level from the 
standard deviation of a sliding window and applying Adaptive Thresholds, the 
data can be segmented in active and rest parts. There is no model 
representation.

@@

*** [discrete and continuous HHMs]

*** Applications of HHM: \cite{shi2009towards} uses 10 coefficients extracted 
with FFT from 6 axis (3 times accelerometer and 3 times gyroscope). Example of 
continuous HMM (?). Recognition rates fo 50\%-100\%.

In \cite{oliver2002layered} it is stated that HMMs are robust mechanisms with 
respect to changes in temporal segmentation of observations, although they 
suffer from a few problems when applied to reason about longer and complexer 
sequences over time. They state that, especially with limited training data, 
the HMM tend to be overfitted and tend to lack structure and have an excess of 
parameters. The overcome this limitation, they introduce a Layered Hidden 
Markov Model (LHHM) which they show is more robust to temporal changes in 
observations. They make use of the hypothesis from the field of psychology, 
that human behavior is hierarchically structured \cite{zacks2001event}. In 
\cite{perdikis2008recognition} a layered construction of HMMs is used which 
feeds the low-level data from a sliding window to the lower layer. This layer 
will recognize simple motions, such as moving the arm in a pre-defined 
segment. The results from these lower HMMs are then fed to a higher-level 
layer of HMMs which are able to recognize abstract motions, such as adjusting 
a monitor and picking up a pen. The results showed that the layered system was 
better at recognition then a similar single-layered setup. It was also robust 
in the sense that when the environment was changed, only the relatively simple 
low-level HMMs needed to be retrained.

*** [DIAGRAM WITH EXAMPLE OF LOW- AND HIGH-LEVEL HMMs, SUCH AS MOVING ARM, 
PICKING UP PEN]

*** Viterbi algorithm / path; find the most likely sequence of cause-states 
for 
the observed measures.
